Quantifying and controlling biases in dark matter halo concentration estimates

### 2016-07-17 paper/ms.tex
drop 6
notation

Using the bootstrapping data we find that at a given normalized
radius, $x$, the logarithm of the normalized integrated mass, $m$, follows a 
distribution that can approximated by a gaussian with variance
\begin{equation}
\sigma_x^2 = \frac{1-x}{x}\frac{1}{6N}.
\label{eq:sigma}
\end{equation}

@@

\begin{equation}
\chi^2(c)= \sum_{i=2}^{N-1}\frac{[\log m_i - \log m(< x_i;c)]^2}{\sigma_i^2},
\end{equation}
%
where $\sigma_i^2=\sigma_x^2$, $m(<x_i;c)$ corresponds to the
values in Eq.(\ref{eq:profile}) at $x=x_i$ for a given value of the
concentration parameter $c$, and the $i$ index sums over all the
particles in the numerical profile. 
In this computation the particles $i=1$ and $i=N$ are discarded to
avoid divergent terms in the sum.

However, tests on the bootstrapping data show that the covariance
matrix is not diagonal and using $\sigma_i^2=\sigma_x^2$ would grossly
overestimate $\chi^2(c)$ providing too optimistic error bars.

@@

We then use $\sigma_i^2=\sigma_{\rm eff}^2$ to feed an Affine
Invariant Markov Chain Monte Carlo implemented in the python module
{\texttt{emcee}} \citep{emcee} to sample the likelihood function
distribution.
From the $\chi^2$ distribution we find the optimal value of the
concentration and its associated uncertainty.

>>>>

Using the bootstrapping data we find that at a given normalized
radius, $x$, the logarithm of the normalized integrated mass, $m$, follows a 
distribution that can approximated by a gaussian with variance
\begin{equation}
\sigma_x^2 = \frac{1-x}{x}\frac{1}{N}.
\label{eq:sigma}
\end{equation}

@@

\begin{equation}
\chi^2(c)= \sum_{i=2}^{N-1}\frac{[\log m_i - \log m(< x_i;c)]^2}{\sigma_i^2},
\end{equation}
%
where $\sigma_i^2=\sigma_x^2(x_i)$, $m(<x_i;c)$ corresponds to the
values in Eq.(\ref{eq:profile}) at $x=x_i$ for a given value of the
concentration parameter $c$, and the $i$ index sums over all the
particles in the numerical profile. 
In this computation the particles $i=1$ and $i=N$ are discarded to
avoid divergent terms in the sum.

However, tests on the bootstrapping data show that the covariance
matrix is not diagonal and using $\sigma_i^2=\sigma_x^2(x_i)$ would grossly
overestimate $\chi^2(c)$ providing too optimistic error bars.

@@

We then use $\sigma_i^2=\sigma_{\rm eff}^2(x_i)$ to feed an Affine
Invariant Markov Chain Monte Carlo implemented in the python module
{\texttt{emcee}} \citep{emcee} to sample the likelihood function
distribution.
From the $\chi^2$ distribution we find the optimal value of the
concentration and its associated uncertainty.
